A Phenomenological Model for the Intracluster Medium that matches X-ray and Sunyaev-Zel'dovich observations

### 2013-10-11 paper1.tex
tosubmit

{\bf In the right panel of Fig.~\ref{fig:SZ_M}, we compare our scaling relation
  to the recent Atacama Cosmology Telescope (ACT) sample
  \citep{2013JCAP...07..008H}, which has a median redshift of $z=0.53$.  Again,
  the slope of our modeled scaling relation is slightly shallower in comparison
  to the observed slope. Most strikingly, there appears to be a 30 per cent
  offset of the scaling relations, which could be due to a number of reasons. On
  the data side, these could include possible selection effects of the different
  cluster samples or possible biases associated with density clumping and/or
  non-thermal pressure contributions inherited from the X-ray informed
  post-processing that was employed by the ACT Collaboration to construct their
  $Y_{500}$ estimates. This could also indicate that our model is too simplistic
  to capture the rich cluster physics and potentially may even point to
  deviations from the assumed self-similar redshift evolution (since the ACT
  sample probes on average higher redshift and less massive clusters in
  comparison to the {\em Planck} sample).  However, note that our scaling
  relation at $z=0.53$ ($A=-27.67\pm0.12$, $B=1.60\pm0.01$) is within the
  uncertainties compatible with that of the ACT sample ($A=-28.59\pm2.26$,
  $B=1.65\pm0.15$).  Thus, we conclude that overall there is reasonable
  agreement between our phenomenological model and the SZ data of the
  \emph{Planck} and ACT collaborations.}

>>>>

{\bf In the right panel of Fig.~\ref{fig:SZ_M}, we compare our scaling relation
  to the recent Atacama Cosmology Telescope (ACT) sample
  \citep{2013JCAP...07..008H}, which has a median redshift of $z=0.53$.  Again,
  the slope of our modeled scaling relation is slightly shallower in comparison
  to the observed slope. Most strikingly, there appears to be a 30 per cent
  offset of the scaling relations, which could be due to a number of reasons. On
  the data side, these could include possible selection effects of the different
  cluster samples or possible biases associated with density clumping and/or
  non-thermal pressure contributions inherited from the X-ray informed
  post-processing that was employed by the ACT Collaboration to construct their
  $Y_{500}$ estimates. This could also indicate that our model is too simplistic
  to capture the rich cluster physics and potentially may even point to
  deviations from the assumed self-similar redshift evolution (since the ACT
  sample probes on average higher redshift and less massive clusters in
  comparison to the {\em Planck} sample).  However, note that our scaling
  relation at $z=0.53$ ($A=-27.67\pm0.12$, $B=1.60\pm0.01$) is within the
  uncertainties compatible with that of the ACT sample ($A=-28.57\pm2.25$,
  $B=1.65\pm0.15$).  Thus, we conclude that overall there is reasonable
  agreement between our phenomenological model and the SZ data of the
  \emph{Planck} and ACT collaborations.}
